---
title: "Analysis of the 'abalone' data"
date: '8 May 2017'
output: ioslides_presentation
---


## Introduction
- This demostration is based on 'abalone' data in R package 'AppliedPredictiveModeling'.
- The considered "lm" model is simple where only one regressor is considered at one time since we would like to illustrate the function of "lm" in a 2-dimensional graph.
- First, you need to choose the desired outcome and regressor from the corresponding list to show a scatterplot.
- Further, you can add the variable "Type" to investigate the variation in different groups.
- The regression line also presents potential features in data.
- You can randomly choose a fraction of the dataset. Otherwise, just slide the bar to 100%.


## Exploratory research on 'abalone' data
```{r,message=FALSE}
library(AppliedPredictiveModeling)
data(abalone)
dim(abalone)
names(abalone)
```

## One illustrative plot: settings

- Percentage of the considered observations: 20%
- Outcome: 'ShuckedWeight'; Regressor: 'ShellWeight'
- Regard 'type' as the condition and include regression lines.
- Code chunk:
```{r,eval=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
numb <-  dim(abalone)[1]
Ndf <- sample_n(abalone, 20 * numb / 100)
dataX <- Ndf$ShellWeight
dataY <- Ndf$ShuckedWeight
dataZ <- Ndf$Type
df <- data.frame(X = dataX, Y = dataY, Z = dataZ)
p <- ggplot(df, aes(x = X,y = Y, colour = Z))
p + geom_point(alpha = .5) + geom_smooth(method = 'lm')
```

## One illustrative plot

```{r,echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
numb <-  dim(abalone)[1]
Ndf <- sample_n(abalone, 20 * numb / 100)
dataX <- Ndf$ShellWeight
dataY <- Ndf$ShuckedWeight
dataZ <- Ndf$Type
df <- data.frame(X = dataX, Y = dataY, Z = dataZ)
p <- ggplot(df, aes(x = X,y = Y, colour = Z))
p + geom_point(alpha = .5) + geom_smooth(method = 'lm')
```


